### 2019-04-09 2-Chapters/5-Chapter/chapter5.tex
Hard to work on this while doing so many other things...

\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Number of players} & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{52 \pm 15}$ & $\mathbf{35 \pm 15}$ & $\mathbf{0}$ \\
        \hline
        \RhoRand-\klUCB{} & $297 \pm 18$ & $1411 \pm 144$ & $2351 \pm 55$ \\
        \RhoRand-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$326 \pm 86$} & \textcolor{red}{$1213 \pm 168$} & \textcolor{red}{$2403 \pm 121$} \\
        \hline
        \RandTopM-\klUCB{} & $188 \pm 18$ & $671 \pm 159$ & $790 \pm 470$ \\
        \RandTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$238 \pm 27$} & \textcolor{red}{$778 \pm 156$} & \textcolor{red}{$1098 \pm 153$} \\
        \hline
        \MCTopM-\klUCB{} & $134 \pm 6$ & $304 \pm 19$ & $42 \pm 5$ \\
        \MCTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$210 \pm 66$} & \textcolor{red}{$465 \pm 39$} & \textcolor{red}{$602 \pm 54$} \\
        \hline
        \Selfish-\klUCB{} & $136 \pm 17$ & $468 \pm 87$ & $1379 \pm 16$ \\
        \hline
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, comparing algorithms which knows $M$ against algorithms which estimate $M$ on the fly.}
    \label{table:5:meanRegretSimulationsEstimatingM}
% \end{footnotesize}
\end{table}

@@

@@

Learning to Coordinate in a Decentralized Cognitive Radio Network in Presence of Jammers
Suneet Sawant, Rohit Kumar, Manjesh K. Hanawal, Sumit J. Darak
https://arxiv.org/abs/1803.06810
\cite{SawantKumar2018}

Note that we have not yet implemented this extension in SMPyBandits \cite{SMPyBandits}, but we are interested to do it, and it is one of the major future work left on our library\footnote{See the issue ticket open at \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{\texttt{GitHub.com/SMPyBandits/SMPyBandits/issues/120}}}.

@@

% FIXME run the simulations with N=100 and not N=4
% for M in 3 6 9; do DEBUG=False SAVEALL=False NOPLOTS=True M=$M K=9 N_JOBS=-1 N=100 T=10000 make moremultiplayers; read; done
\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithm} $\;$ \textbackslash $\;$ Number of players & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{93 \pm 15}$ & $\mathbf{72 ± 19}$ & $\mathbf{0}$ \\
        \hline
        \RhoRand-\klUCB{} & $429 \pm 134$ & $2451 ± 338$ & $6044 ± 744$ \\
        \texttt{rhoLearn}-\klUCB{} + \klUCB{} & $473 \pm 141$ & $1277 ± 535$ & $1193 ± 303$ \\
        \texttt{rhoLearn}-\klUCB{} + Bayes-UCB & $473 \pm 141$ & $1277 ± 535$ & $1158 ± 133$ \\
        \texttt{rhoLearn}-\klUCB{} + Exp3 & $548 \pm 176$ & $1880 ± 389$ & $5222 ± 813$ \\
        \hline
        \MCTopM-\klUCB{} & $269 \pm 34$ & $401 ± 36$ & $39 ± 3$ \\
        \hline
    \end{tabular}
    \caption{Comparison of \RhoRand{} and \texttt{rhoLearn} for a simple multi-player bandit problem with $K=9$ arms.}
    \label{table:5:comparisonRhoRandRhoLearn}
% \end{footnotesize}
\end{table}

>>>>

\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Number of players} & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{92 \pm 20}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0}$ \\
        \hline
        \RhoRand-\klUCB{} & $417 \pm 103$ & $2481 \pm 449$ & $2351 \pm 55$ \\
        \RhoRand-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$1422 \pm 1051$} & \textcolor{red}{$9030 \pm 1922$} & \textcolor{red}{$2403 \pm 121$} \\
        \hline
        \RandTopM-\klUCB{} & $268 \pm 45$ & $941 \pm 217$ & $790 \pm 470$ \\
        \RandTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$688 \pm 614$} & \textcolor{red}{$4256 \pm 2701$} & \textcolor{red}{$1098 \pm 153$} \\
        \hline
        \MCTopM-\klUCB{} & $244 \pm 39$ & $401 \pm 55$ & $42 \pm 5$ \\
        \MCTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$563 \pm 546$} & \textcolor{red}{$1560 \pm 1293$} & \textcolor{red}{$602 \pm 54$} \\
        \hline
        \Selfish-\klUCB{} & $250 \pm 34$ & $735 \pm 85$ & $1379 \pm 16$ \\
        \hline
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, comparing algorithms which knows $M$ against algorithms which estimate $M$ on the fly.}
    \label{table:5:meanRegretSimulationsEstimatingM}
% \end{footnotesize}
\end{table}

@@

In all this chapter and the previous research literature, another common hypothesis is that all the $M$ players are pursuing the same goal, and are all behaving nicely by following the same algorithm.
% Efficient utilization of licensed spectrum in the cognitive radio network is challenging due to lack of coordination among the Secondary Users (SUs).
Distributed algorithms proposed in the literature aim to maximize the network throughput by ensuring orthogonal channel allocation for the SUs.
However, these algorithms work under the assumption that all the SUs faithfully follow the algorithms which may not always hold due to the decentralized nature of the network.
In the paper \cite{SawantKumar2018}, the authors study for the first time distributed algorithms that are robust against malicious behavior, also called \emph{jamming attack}.
They consider both the cases of jammers launching coordinated and uncoordinated attacks, and consider a set of $J$ jammers.
In the coordinated attack, the jammers select non-overlapping channels to attack in each time slot and can significantly increase the number of collisions for SUs.
They setup the problem in each scenario as a multi-player bandit and develop algorithm,
and their analysis shows that when the SUs faithfully implement proposed algorithms, the regret is constant with high probability.
They validate their claims through exhaustive synthetic experiments and also through a realistic USRP.
Their synthetic experiments consider different cases, for different values of $K$ the number of channels, $M$ the number of players and $J$ the number of jammers.

@@

Note that we have not yet implemented this extension in SMPyBandits \cite{SMPyBandits}, but we are interested to do it, and it is one of the major future work left on our library\footnote{See the issue ticket open at \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{\texttt{GitHub.com/SMPyBandits/SMPyBandits/issues/120}}}.
It would not be too difficult to do, we just lacked some time.

@@

% FIXME run the simulations with N=100 and not N=4
% for M in 3 6 9; do DEBUG=False SAVEALL=False NOPLOTS=True M=$M K=9 N_JOBS=-1 N=100 T=10000 make moremultiplayers; read; done
\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithm} $\;$ \textbackslash $\;$ Number of players & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{92 \pm 20}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0}$ \\
        \hline
        \RhoRand-\klUCB{} & $417 \pm 103$ & $2481 \pm 449$ & $6044 \pm 744$ \\
        \hline
        \texttt{rhoLearn}-\klUCB{} + \klUCB{} & $546 \pm 190$ & $1172 \pm 295$ & $1193 \pm 303$ \\
        \texttt{rhoLearn}-\klUCB{} + Bayes-UCB & $561 \pm 219$ & $1204 \pm 394$ & $1158 \pm 133$ \\
        \texttt{rhoLearn}-\klUCB{} + Exp3 & $529 \pm 175$ & $1659 \pm 331$ & $5222 \pm 813$ \\
        \hline
        \MCTopM-\klUCB{} & $244 \pm 39$ & $401 \pm 55$ & $39 \pm 3$ \\
        \hline
    \end{tabular}
    \caption{Comparison of \RhoRand{} and \texttt{rhoLearn} for a simple multi-player bandit problem with $K=9$ arms.}
    \label{table:5:comparisonRhoRandRhoLearn}
% \end{footnotesize}
\end{table}
